Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-10 Article.tex
Change Xdrx to Xdrx predicted in last paragraph

Temperature and strain rate are critical factors that influence dynamic recrystallization in materials, particularly metals and alloys.
This process leads to the formation of new grains within the material.
Higher temperatures and lower strain rates typically result in increased nucleation rates and faster growth rates of new grains during dynamic recrystallization.
Conversely, lower temperatures and higher strain rates can lead to incomplete dynamic recrystallization.
At high temperatures, the increased mobility of both atoms and dislocations facilitates the formation of fresh grain boundaries and promotes the growth of new grains, resulting
in a more refined and isotropic grain structure.
In addition, higher temperatures can raise the proportion of recrystallized material, with the enhanced dislocation mobility contributing to new grain creation.
Consequently, this may result in a substantial change of the microstructure and the mechanical properties of the material.
Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} display the simulated results of the DRX fraction of P20 steel under different deformation conditions.
Figure \ref{fig:TempEffect} shows that as the temperature increases, the extent of dynamic recrystallization widens.
The gradual increase in the dynamic recrystallization fraction in the center is noticeable, spreading outward.
This expansion is a result of higher thermal activation and increased atomic diffusion at higher temperatures, which makes the material more vulnerable to dynamic recrystallization.
The dynamic recrystallization degree ($X_{drx}$) unequivocally grows with the increase in temperature and reduction.
At $45\%$ and $60\%$ reduction, the $X_{drx}$ of P20 steel
attained $100\%$ in the center of the specimen at all the initial sample temperatures.
Indeed, the plastic deformation of a material is accompanied by the creation of dislocations.
These dislocations represent a "storage of elastic energy".
When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganization of the crystal structure in two stages: restoration and recrystallization.
The nature of the phases remains unchanged (those that are thermodynamically stable), and the atoms retain the same lattice.
However, the grain boundaries and the orientation of the crystallites undergo changes.

\begin{figure}[H]
\centering
\includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
\caption{$X_{drx}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
\label{fig:TempEffect}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[height=0.6\columnwidth]{Figures/SR_DRX}
\caption{$X_{drx}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
\label{fig:SREffect}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
\label{fig:expNumDRX}
\end{figure}

\textcolor{purple}{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level. It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape. As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}$ is less than $5\%$ and the microstructure enhances very large grains. We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}$ is in the range of $75\%$ to $90\%$.}
\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
\label{fig:expNumDRX2}
\end{figure}

@@

\noindent
\begin{tabular}{@{}ll}
ANN & Artificial neural network \\
AR  & Arrhenius \\
CPU & Central processing unit \\
DRC & Dynamic recovery\\
DRX & Dynamic recrystallization \\
$X_{drx}^{e,p}$ & DRX's Volume fraction : $e, p$ for experimental and prediction respectively \\
FE  & Finite Element \\
HS  & Hansel--Spittel \\
JC  & Johnson--Cook \\
MZA & Modified Zerilli--Armstrong \\
SRX & Static recrystallization \\
WH  & Work hardening \\
ZA  & Zerilli--Armstrong
\end{tabular}
}

>>>>

Temperature and strain rate are critical factors that influence dynamic recrystallization in materials, particularly metals and alloys.
This process leads to the formation of new grains within the material.
Higher temperatures and lower strain rates typically result in increased nucleation rates and faster growth rates of new grains during dynamic recrystallization.
Conversely, lower temperatures and higher strain rates can lead to incomplete dynamic recrystallization.
At high temperatures, the increased mobility of both atoms and dislocations facilitates the formation of fresh grain boundaries and promotes the growth of new grains, resulting
in a more refined and isotropic grain structure.
In addition, higher temperatures can raise the proportion of recrystallized material, with the enhanced dislocation mobility contributing to new grain creation.
Consequently, this may result in a substantial change of the microstructure and the mechanical properties of the material.
Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} display the simulated results of the DRX fraction of P20 steel under different deformation conditions.
Figure \ref{fig:TempEffect} shows that as the temperature increases, the extent of dynamic recrystallization widens.
The gradual increase in the dynamic recrystallization fraction in the center is noticeable, spreading outward.
This expansion is a result of higher thermal activation and increased atomic diffusion at higher temperatures, which makes the material more vulnerable to dynamic recrystallization.
The dynamic recrystallization degree ($X_{drx}^{p}$) unequivocally grows with the increase in temperature and reduction.
At $45\%$ and $60\%$ reduction, the $X_{drx}^{p}$ of P20 steel
attained $100\%$ in the center of the specimen at all the initial sample temperatures.
Indeed, the plastic deformation of a material is accompanied by the creation of dislocations.
These dislocations represent a "storage of elastic energy".
When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganization of the crystal structure in two stages: restoration and recrystallization.
The nature of the phases remains unchanged (those that are thermodynamically stable), and the atoms retain the same lattice.
However, the grain boundaries and the orientation of the crystallites undergo changes.

\begin{figure}[H]
\centering
\includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
\caption{$X_{drx}^{p}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
\label{fig:TempEffect}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[height=0.6\columnwidth]{Figures/SR_DRX}
\caption{$X_{drx}^{p}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
\label{fig:SREffect}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}^{p}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
\label{fig:expNumDRX}
\end{figure}

\textcolor{purple}{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level. It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape. As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}^{p}$ is less than $5\%$ and the microstructure enhances very large grains. We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75\%$ to $90\%$.}
\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
\label{fig:expNumDRX2}
\end{figure}

@@

\noindent
\begin{tabular}{@{}ll}
ANN & Artificial neural network \\
%AR  & Arrhenius \\
%CPU & Central processing unit \\
%DRC & Dynamic recovery\\
DRX & Dynamic recrystallization \\
$X_{drx}^{e,p}$ & DRX's Volume fraction : $e, p$ for experimental and prediction respectively \\
FE  & Finite Element \\
%HS  & Hansel--Spittel \\
%JC  & Johnson--Cook \\
%MZA & Modified Zerilli--Armstrong \\
SRX & Static recrystallization \\
WH  & Work hardening
%ZA  & Zerilli--Armstrong
\end{tabular}
}
